Boundary Labeling for annotated documents

### 2018-04-11 LaTeX/Paper.tex
Paper: Updated system specs. Program: No changes.

All tests were run under 64-bit Windows 7 on a dual-core laptop\footnote{Dell Latitude E6400, Intel Core2 Duo, 4047 MB Virtual Memory on a SSD}.

@@

\begin{figure}
	\centering
	\begin{subfigure}[b]{\textwidth}
		\centering
		\includegraphics[page=1, scale=0.50]{Rplots_n(5-0).pdf}
		\caption{\label{fig:plot1_n5,0}}
	\end{subfigure}
	\\
	~\\%There's probably a better way to force multiple newlines...
	\begin{subfigure}[b]{\textwidth}
		\centering
		\includegraphics[page=1, scale=0.50]{Rplots_n(5-0)_repeat.pdf}
		\caption{\label{fig:plot2_n5,0}}
	\end{subfigure}
	\caption{Two plots of the same test seed's time taken per text. Note the massive differences caused by the computer's scheduling.}
	\label{fig:timeplot}
\end{figure}

>>>>

All tests were run under 64-bit Windows 7 Professional Version 6.1.7601 Service Pack 1 Build 7601 on a consumer-grade laptop using Java 1.8.0u40. The laptop is a Dell Latitude E6400 with an Intel Core2 Duo dual-core processor running at 2.53 GHz and 4 GB DDR2 RAM. There's 4047 MB virtual memory available on the SSD as well.

@@

\begin{figure}
	\centering
	\begin{subfigure}[b]{\textwidth}
		\centering
		\includegraphics[page=1, scale=0.50]{Rplots_n(5-0).pdf}
		\caption{\label{fig:plot1_n5,0}}
	\end{subfigure}

	\begin{subfigure}[b]{\textwidth}
		\centering
		\includegraphics[page=1, scale=0.50]{Rplots_n(5-0)_repeat.pdf}
		\caption{\label{fig:plot2_n5,0}}
	\end{subfigure}
	\caption{Two plots of the same test seed's time taken per text. Note the massive differences caused by the computer's scheduling.}
	\label{fig:timeplot}
\end{figure}
